---
output: rmarkdown::github_document
---
`hrbrthemes` : Additional Themes and Theme Components for 'ggplot2'

This is a very focused package that provides typography-centric themes and theme components for ggplot2. It's a an extract/riff of [`hrbrmisc`](http://github.com/hrbrmstr/hrbrmisc) created by request. 

The core theme: `theme_ipsum` ("ipsum" is Latin for "precise") uses Arial Narrow which should be installed on practically any modern system, so it's "free"-ish. This font is condensed, has solid default kerning pairs and geometric numbers. That's what I consider the "font trifecta" must-have for charts. An additional quality for fonts for charts is that they have a diversity of weights. Arial Narrow (the one on most systems, anyway) does not have said diversity but this quality is not (IMO) a "must have".

The following functions are implemented/objects are exported:

- `theme_ipsum` : Arial Narrow-based theme
- `theme_ipsum_rc` : Roboto Condensed-based theme
- `update_geom_font_defaults`:	Update matching font defaults for text geoms (the default is — unsurprisingly — Arial Narrow)
- `scale_x_comma` / `scale_y_comma` : Comma format for axis text and `expand=c(0,0)` (you need to set limits)
- `scale_x_percent` / `scale_y_percent` : Percent format for axis text and `expand=c(0,0)` (you need to set limits)
- `font_an`: a short global alias for "`Arial Narrow`"
- `font_rc`: a short global alias for "`Roboto Condensed`"
- `font_rc_light`: a short global alias for "`Roboto Condensed Light`"

### TODO

- Creation of supplemental extra font packages with instructions for installation
- Additional base themes to match ^^
- At least one new custom color & fill scale
- Whatever ends up in a feature request in an issue that makes sense ;-)

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/hrbrthemes")
```

```{r message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(hrbrthemes)
library(tidyverse)

# current verison
packageVersion("hrbrthemes")
```

### Base theme (Arial Narrow)

```{r fig.retina=2}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
       title="Seminal ggplot2 scatterplot example",
       subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by the letter 'g'") + 
  theme_ipsum()
```

### Roboto Condensed

```{r fig.retina=2}
ggplot(mtcars, aes(mpg, wt)) +
  geom_point() +
  labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
       title="Seminal ggplot2 scatterplot example",
       subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by the letter 'g'") + 
  theme_ipsum_rc()
```

### Scales

```{r fig.retina=2}
count(mpg, class) %>% 
  mutate(pct=n/sum(n)) %>% 
  ggplot(aes(class, pct)) +
  geom_col() +
  scale_y_percent() +
  labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
       title="Seminal ggplot2 column chart example with percents",
       subtitle="A plot that is only useful for demonstration purposes",
       caption="Brought to you by the letter 'g'") + 
  theme_ipsum(grid="Y")
```

```{r fig.retina=2}
update_geom_font_defaults(font_rc_light)

count(mpg, class) %>% 
  mutate(n=n*2000) %>% 
  arrange(n) %>% 
  mutate(class=factor(class, levels=class)) %>% 
  ggplot(aes(class, n)) +
  geom_col() +
  geom_text(aes(label=scales::comma(n)), hjust=0, nudge_y=2000) +
  scale_y_comma(limits=c(0,150000)) +
  coord_flip() +
  labs(x="Fuel effiiency (mpg)", y="Weight (tons)",
       title="Seminal ggplot2 column chart example with commas",
       subtitle="A plot that is only useful for demonstration purposes, esp since you'd never\nreally want direct labels and axis labels",
       caption="Brought to you by the letter 'g'") + 
  theme_ipsum_rc(grid="X")
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(hrbrthemes)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.